\documentclass{sig-alternate}
\input{macros}
\usepackage{subfloat}
\pagestyle{empty}
\usepackage{ifpdf}
\usepackage{multicol}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{graphicx}
\pagenumbering{roman}
\usepackage{textcomp}
\usepackage{fixltx2e}
\usepackage{listings}
\usepackage[table]{xcolor}	
\usepackage[caption=false]{subfig}
\begin{document}
\conferenceinfo{ICPE'12,} {April 22-25, 2012, Boston, Massachusetts, USA}
\CopyrightYear{2012}
\crdata{978-1-4503-1202-8/12/04}
\clubpenalty=10000
\widowpenalty = 10000
\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\numberofauthors{5}
\title{Refactoring Access Control Policies for Performance Improvement}
\author{
\alignauthor Donia El Kateb \\
\affaddr{Laboratory of Advanced Software SYstems (LASSY)}
 \affaddr{University of Luxembourg} \\
 \affaddr{Luxembourg } \\
 \email{donia.elkateb@uni.lu}
\alignauthor Tejeddine Mouelhi \\
 \affaddr{Security, Reliability and
Trust Interdisciplinary
Research Center, SnT}\\
 \affaddr{University of Luxembourg} \\
 \affaddr{Luxembourg } \\
 \email{tejeddine.mouelhi@uni.lu}
\alignauthor Yves Le Traon \\
\affaddr{Laboratory of Advanced Software SYstems (LASSY) \& Security, Reliability and
Trust Interdisciplinary Research Center, SnT}\\
 \affaddr{University of Luxembourg} \\
 \affaddr{Luxembourg} \\
 \email{yves.letraon@uni.lu}
\and  
\alignauthor JeeHyun Hwang \\
\affaddr{Dept. of Computer Science
} \\
\affaddr{North Carolina State University} \\
 \affaddr {U.S.A} \\
 \email{jhwang4@ncsu.edu}
\alignauthor Tao Xie \\
\affaddr{Dept. of Computer Science
} \\
\affaddr{North Carolina State University} \\
 \affaddr {U.S.A} \\
 \email{xie@csc.ncsu.edu}
}
\maketitle
\begin{abstract}
In order to facilitate managing authorization, access control architectures are designed to separate the business logic from an access control policy. 
An access control policy consists of 
rules that specify who has access to resources. A request is formulated from a component, called a Policy Enforcement Point (PEP). 
Given a request, a Policy Decision Point (PDP) evaluates the request against an access control policy and
returns its access decision (i.e., Permit or Deny) to the PEP.
With the growth of sensitive information for protection in an application,
an access control policy consists of a larger number of rules, which often cause a performance bottleneck. 
To address this issue, we propose to refactor access control policies for performance improvement by splitting a policy (handled by a single PDP) into its corresponding multiple policies with a smaller number of rules (handled by multiple PDPs).
We define seven attribute-set-based splitting criteria to facilitate splitting a policy.
We have conducted an evaluation on three subjects of real-life Java systems, each of which interacts with access control policies. Our evaluation results show that (1) our approach preserves the initial architectural model in terms of 
interaction between the business logic and its corresponding rules in the policy, and (2) our approach enables to reduce request evaluation time by up to nine times. 
 \end{abstract}
\category{C.4}{Performance of systems}{Performance attributes}\\
\category{D.4.8}{Performance}{Measurements}
\terms{Performance, Design}
\keywords{Access Control, Performance, Refactoring, Policy Enforcement Point, Policy Decision Point, eXtensible Access Control Markup Language}
\input{intro}
\input{background}
\input{approach}
\input{experiment}
\input{related}
\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{sigproc} 
\balancecolumns
\end{document}